Automated data-driven symbolic modeling of the lift forces acting on flapping wings

### 2021-01-19 paper/main.tex
Move Methods section after Introduction
Move schematic diagram into Methods section and add introductory paragraph to Methods section

@@

\begin{figure}%[!htb]
\centering
\begin{subfigure}{0.3\textwidth}
\includegraphics[trim=0 15 0 5, clip, width=\textwidth]{figures/apparatus}
\caption{\label{fig:apparatus}}
\end{subfigure}
\qquad
\begin{subfigure}{0.5\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/mae_nofit}
\caption{\label{fig:pareto_mae}}
\end{subfigure}
\caption{\subref{fig:apparatus} Schematic diagram of the experimental apparatus
  showing three kinematic variables of the wing motion: stroke ($\phi$),
  deflection ($\psi$) and deviation ($\theta$). \subref{fig:pareto_mae} Pareto
  plot of all data-driven (``EQ Models'') and analytical models using mean
  values for model coefficients. All data-driven models were smaller and more
  accurate than analytical models.
}
\end{figure}

@@

\section*{Methods}

>>>>

\section*{Methods}
Our experimental apparatus consisted of a wing and actuator mounted to a
vertical force sensor, with a high-speed video camera recording the motion of
the wing from a top-down view and (using a mirror) also from a side-view.
Figure~\ref{fig:apparatus} provides a diagram of the apparatus as well as
illustrations of the three primary variables describing the orientation of the
wing in the apparatus: Stroke ($\phi$), deflection ($\psi$) and deviation
($\theta$). The stroke motion is enabled by a hinge joint and is the only
actuated degree of freedom in the system. The deflection of the wing is enabled
by a hinge in the root of the wing, and is a passive motion resulting from both
inertial and aerodynamic effects. Deviation refers to the passive vertical
motion of the wing out of its horizontal flapping plane, and is enabled only by
the tolerances of the hinges and the flexibility of the wing structure itself.

\begin{figure}
\centering
\includegraphics[trim=0 15 0 5, clip, width=0.5\textwidth]{figures/apparatus}
\caption{Schematic diagram of the experimental apparatus
  showing three kinematic variables of the wing motion: stroke ($\phi$),
  deflection ($\psi$) and deviation ($\theta$).\label{fig:apparatus}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figures/mae_nofit}
\caption{Pareto plot of all data-driven (``EQ Models'') and analytical models
  using mean values for model coefficients. All data-driven models were smaller
  and more accurate than analytical models.\label{fig:pareto_mae}}
\end{figure}

@@
